Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-13 manuscript/manuscript.tex
minor formatting
Continue Results

\begin{table}[ht]
    \caption{Descriptive Statistics of Healthcare Diabetes Dataset}
  \label{tab:ds}
\centering
\begin{tabular}{lrrr}
      \hline
    Variable & Mean & SD & Median \\ 
      \hline
      Pregnancies & 3.74 & 3.32 & 3.00 \\ 
      Glucose & 121.10 & 32.04 & 117.00 \\ 
      BloodPressure & 69.13 & 19.23 & 72.00 \\ 
      SkinThickness & 20.82 & 16.06 & 23.00 \\ 
      Insulin & 80.13 & 112.30 & 37.00 \\ 
      BMI & 32.14 & 8.08 & 32.20 \\ 
      DiabetesPedigreeFunction & 0.47 & 0.33 & 0.38 \\ 
      Age & 33.13 & 11.78 & 29.00 \\ 
       \hline
    \end{tabular}
    \end{table}
  Another valuable piece of information for understanding our patients is seeing the range of the dataset. In Figure~\ref{fig:histogram}, we
  are able to see the spread of each predictor in our dataset. We can see that the majority of our patients are in the 20 to 30 year old range. 
  The bloodpressure predictor provides us with a somewhat normal distribution with the average being around 70 beats per minute. The BMI
  distribution is somewhat normal as well, with a slight right skew. Whereas the diabetes pedigree function is very skewed to the right. Glucose
  levels appear to be normal. Insulin levels appear to be very skewed to the right with the majority of values being 0. The outcome distribution
  is exactly as expected with only values of 0 or 1, from here on values of 0 will denote no detection of diabetes and 1 will detect diabetes. The
  number of pregnancies predictor also supplied a right skew but we know this to be valid as most people are not having 4 or more children. The 
  final predictor graphed was the skin thickness, this predictor displayed a right skew.

@@

>>>>

\begin{table}[ht]
    \caption{Descriptive Statistics of Healthcare Diabetes Dataset}
  \label{tab:ds}
\centering
\begin{tabular}{lrrr}
      \hline
    Variable & Mean & SD & Median \\ 
      \hline
      Pregnancies & 3.74 & 3.32 & 3.00 \\ 
      Glucose & 121.10 & 32.04 & 117.00 \\ 
      BloodPressure & 69.13 & 19.23 & 72.00 \\ 
      SkinThickness & 20.82 & 16.06 & 23.00 \\ 
      Insulin & 80.13 & 112.30 & 37.00 \\ 
      BMI & 32.14 & 8.08 & 32.20 \\ 
      DiabetesPedigreeFunction & 0.47 & 0.33 & 0.38 \\ 
      Age & 33.13 & 11.78 & 29.00 \\ 
       \hline
    \end{tabular}
    \end{table}

  Another valuable piece of information for understanding our patients is seeing the range of the dataset. In Figure~\ref{fig:histogram}, we
  are able to see the spread of each predictor in our dataset. We can see that the majority of our patients are in the 20 to 30 year old range. 
  The bloodpressure predictor provides us with a somewhat normal distribution with the average being around 70 beats per minute. The BMI
  distribution is somewhat normal as well, with a slight right skew. Whereas the diabetes pedigree function is very skewed to the right. Glucose
  levels appear to be normal. Insulin levels appear to be very skewed to the right with the majority of values being 0. The outcome distribution
  is exactly as expected with only values of 0 or 1, from here on values of 0 will denote no detection of diabetes and 1 will detect diabetes. The
  number of pregnancies predictor also supplied a right skew but we know this to be valid as most people are not having 4 or more children. The 
  final predictor graphed was the skin thickness, this predictor displayed a right skew.

@@

Looking at Table~ref{tab:dtr}, we can see that the accuracy of our model is 0.82, this is pretty high so it will be satisfactory. This tells us that we 
classify correctly 82 percent of the time out of the total instances. The next metric we will look at is precision, we were able to get to 72 percent.
This is the ratio of correctly predicted positive observations to the total predicted positives. Looking at recall, we were able to correctly identify about
74 percent of the actual positive instances. This is pretty good and will be considered satisfactory. The final metric that we have is the F1 score, this is the
harmonic mean of precision and recall, which we were able to get a value of 0.73, this indicates a balanced performance.
